\documentclass{ximera}

\title{Section 3.4 Systems of Linear Equations}
\author{Conner Griffin}

\begin{document}
\begin{abstract}
    We solve systems of linear equations in two and three variables using elimination and substitution.
\end{abstract}
\maketitle

The set of solutions to the equation \(2x+4y =3\) form a straight line. There are few ways that we can express the solutions to this system. If we solve for \(y\) we get \(y = -\frac{1}{2}x + \frac{3}{4}.\) Then every solution as an order pair looks like \(\left(x, -\frac{1}{2}x + \frac{3}{4}\right).\) A graph of this line.

\desmos{b6wly9f2la}{100}{600}

What if we want all \((x,y)\) that satisfy two equations at once!

\begin{example}
    What do solutions to
    \[\begin{cases}
        2x+4y=3 \\
        -x+y =2
    \end{cases}\]
    look like?

    The following is a graph of solutions to both equations.

    \desmos{mnpol53mao}{100}{600}

    The only solution to both equations is the point of interesection for the two lines. In this case, \(\left(-5/6,7/6\right)\)
\end{example}

\input{matrixAlgebra/systemOfLinearEquations/definitions/defSystemOfEquations}
\input{matrixAlgebra/systemOfLinearEquations/examples/exSystemOfEquations}
\input{matrixAlgebra/systemOfLinearEquations/definitions/defSystemOfLinearEquations}
\input{matrixAlgebra/systemOfLinearEquations/examples/exSystemOfLinearEquations}
\input{matrixAlgebra/systemOfLinearEquations/examples/exZeroOneInfinitely}
\input{matrixAlgebra/systemOfLinearEquations/examples/exSolvingSystemsByElimination}
\end{document}