\documentclass{ximera}

\title{Section 5.3 Interest Compounded Continuously}
\author{Conner Griffin}

\begin{document}
\begin{abstract}
    In many cases, interest compounds ``continuously'' meaning that interest is being applied constantly rather than periodically. We present a formula for continuously compounding interest and a corresponding present value formula.
\end{abstract}
\maketitle

When interest is compounding with a frequency \(k,\) interest is only applied to the principal at the end of the interest period. The following graph illustrates the graph of the value of an account over time in which \(\$1000\) is invested at \(3.5\%\) compounding annually. The \(x\)-axis is time in years and the \(y\)-axis is dollar amount in \(\$1000.\)

\desmos{zezbdwqwzc}{100}{600}

We need to determine what happens when we comound interest continuously. To do so, we will need to apply the following fact. As \(n\) goes towards infinity, \(\left(1+\frac{1}{n}\right)^n\) gets closer and closer to \(e,\) Euler's constant.

\desmos{dzkorb9ggc}{100}{600}

Interest that compounds with annual frequency \(k\) at annual rate \(r\) is calculated with the formula,

\[S= P\left(1+\frac{r}{k}\right)^{kt}\]

where \(kt\) is the number of interest periods that go by.

If interest is compounding continuously, then we are letting the annual compounding frequency go to infinity.

Rewriting our formula,

\[P\left(1+\frac{r}{k}\right)^{kt} = P\left(\left(1+\frac{r}{k}\right)^{\frac{k}{r}}\right)^{rt} = P\left(\left(1+\frac{1}{k/r}\right)^{\frac{k}{r}}\right)^{rt}.\]

Letting \(n=\frac{k}{r}.\) We note that \(n\) is going to infinity with \(k\) and that

\[P\left(\left(1+\frac{1}{k/r}\right)^{\frac{k}{r}}\right)^{rt}=P\left(\left(1+\frac{1}{n}\right)^{n}\right)^{rt}\]

is going to 

\[Pe^{rt}.\]

\input{definitions/defContinuouslyCompoundingInterest}
\input{examples/exCompoundAmount}
\input{definitions/defEffectiveRateContinuous}
\input{examples/exEffectiveRateContinuous}
\input{definitions/defPresentValueContinuous}
\input{examples/exPresentValueContinuous}

\end{document}