\begin{definition}
    An \emph{exponential function} is a function \(f\) which may be defined by
    \[f(x) = b^x\]
    for some positive real number \(b>0\) with \(b \ne 1.\)
\end{definition}

Let's recall some rules for exponents!
For the following rules let \(x,y\) be arbitrary real numbers, let \(a,b\) be positive non-one real numbers, and let \(n\) be a positive integer.
\begin{enumerate}
    \item \(b^xb^y = b^{x+y}\)
    \item \(b^{xy} = \left(b^{x}\right)^y\)
    \item \(\left(ab\right)^{x} = a^xb^x\)
    \item \(\frac{1}{b^x} = b^{-x}\)
    \item \(b^0 = 1\)
    \item \(b^1 = b\)
    \item \(b^2=b\cdot b\)
    \item \(b^n = b\cdot \dots \cdot b\) (here we have multiplied \(b\) exactly \(n\) times)
    \item \(b^{1/n}\) is the unique positive real number solution to the equation \(x^n = b\)
\end{enumerate}

It is worth asking ``what is meant by the expression \(2^{\sqrt{2}}?\)'' Since \(\sqrt{2}\) is not rational it does not make sense to talk about \(2^{\sqrt{2}}\) in terms of roots of polynomial equations. Numbers which are not rational may be approximated as close as we like by rational numbers. For example if we want to be within \(\frac{1}{100}\)th of \(\sqrt{2}\) we may take \(\frac{17}{12} = 1.41\overline{6}\) as our approximation. If we want to be within \(\frac{1}{100 000}\)th of \(\sqrt{2}\) then we may take \(\frac{577}{408} = 1.414\overline{2156862745098039}.\) Indeed, an accurate approximation of \(\sqrt{2}\) within \(10^{-10}\) would be \(1.4142135623.\) At the time of authorship, \(28\) trillion digits of \(\sqrt{2}\) have been calculated. See this \href{https://web.archive.org/web/20260213030310/https://www.numberworld.org/y-cruncher/records.html}{website} for details on this world record. Any rational power of two can be expressed as a solution to a polynomial equation! For example, \(2^{\frac{17}{12}} = \left(2^{17}\right)^{\frac{1}{12}}\) by rule \(2\) above. Then this number is the unique positive solution to \(x^{12}=2^{17}.\) Using these approximations of \(\sqrt{2}\) we can determine a unique value for \(2^{\sqrt{2}}.\)