\begin{question}
    Consumers will buy \(q\) units of a product at a price of \(\frac{300}{q}+15\) dollars per unit. What is the minimum number of units that must be sold so that sales revenue is greater than \(\$9450?\)

    \begin{solution}
    \(\textrm{Revenue} = \textrm{Quantity}\cdot\textrm{Price} = q \left(\frac{300}{q}+15\right).\)
    Revenue is greater than \(\$ 9450.\) We need to solve for \(q\) given that \[q \left(\frac{300}{q}+15\right) > 9450.\]
    \begin{gather*}
        q \left(\frac{300}{q}+15\right) > 9450\\
        300+15q>9450 \\
        15q > 9150 \\
        q> 610
    \end{gather*}
    The manufacturer needs to produce at least \(611\) units for the revenue to be greater than \(\$9450.\)
    \end{solution}
\end{question}

Why was the answer not \(610?\) If the manufacturer produced \(610\) units then the total revenue is exactly \(\$9450\) which is \emph{not} greater than itself.

\begin{question}
    You have \(\$50,000\) to spend producing units. The fixed cost is \(\$7500.\) The variable cost per unit is \(\$270.\) What is the greatest number of units that you can afford to produce?
    
    \begin{solution}
        Let \(q\) be the quantity of units produced. Then \(VC = 270q\) and thus
        \(\textrm{C} = \textrm{FC} + 270q.\)
        We need that cost is less than or equal to \(50,000.\)
        \begin{gather*}
            7500+270q \le 50000 \\
            270q \le 42500 \\
            q \le \frac{4250}{27} \approx 157.41
        \end{gather*}
    \end{solution}
    The greatest number of units you can purchase is \(157.\)
\end{question}

\begin{question}
    A widget manufacturer produces \(q\) widgets. The total labor cost is \(\$12q,\) and the total material cost is \(\$5q.\) The fixed cost is \(\$130,000.\) If each widget sells for \(\$70,\) how many widgets must be produced and sold so that the manufacturer realizes a profit?
    
    \begin{solution}
        Ultimately we need to calculate a our profit dependent on \(q.\) To calculate profit we need to know revenue and cost. Revenue is \(70q\) and cost is fixed cost plus variable cost. Suppose there are no other variable costs. Then cost is \(12q+5q+130000 = 17q+130000.\)
        Our profit formula,
        \[P = 70q-(17q+130000) = 53q-130000,\]
        needs to be greater than \(0\) for a profit to be realized.
        \begin{gather*}
            53q-130000>0 \\
            53q>130000 \\
            q> \frac{130000}{53} \approx 2452.83
        \end{gather*}
        The manufacturer must produce at least \(2453\) units to realize a profit.
    \end{solution}
\end{question}
